Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-14 phd-cs-us.tex

Additionally, \textbf{work experiences at renowned research laboratories}, such as Microsoft Research, can significantly strengthen your
application.  Unfortunately, many good research places in your countries, e.g., VinAI in Vietnam, remain relatively unknown to most universities in the US. So you should explicit say something about them in your statement.

@@

\subsection{Tenured or tenure-track faculty? Who do you choose?}

The short answer is that tenured-track faculty (e.g., assistant professors) are more likely to be young and very active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. The downside is that they may not have as much experience in managing students and may not have as much funding as tenured faculty.
Tenured faculty (e.g., associate and full profs.) are more likely to be older, more well-known, and have more experience in managing students.  However, they might not push you as hard (they don't have to, they already got tenured) and expect you to figure things out yourself (so you need to be very independent).  Some tenured faculty are also no longer active in research, e.g., they are more involved in administrative duties.

>>>>

Additionally, \textbf{work experiences at renown research laboratories}, such as Microsoft Research, can significantly strengthen your
application.  Unfortunately, many good research places in your countries, e.g., VinAI in Vietnam, remain relatively unknown to most universities in the US. So you should explicit say something about them in your statement.

@@

\subsection{Tenured or tenure-track faculty? Who do you choose?} 
The short answer is that tenured-track faculty (e.g., assistant professors) are more likely to be young and very active in research (they have to, in order to get tenure). Thus, they will likely have more time to work with you and push you to do research and publish. The downside is that they may not have as much experience in managing students and may not have as much funding as tenured faculty.
Tenured faculty (e.g., associate and full profs.) are more likely to be older, more well-known, and have more experience in managing students.  However, they might not push you as hard (they don't have to, they already got tenured) and expect you to figure things out yourself (so you need to be very independent).  Some tenured faculty are also no longer active in research, e.g., they are more involved in administrative duties.
